Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: wording in conclusion
BCP: we refine a library, not a file
Use \subsubsections for steps in BCP
BCP: wording

This section shows how behaviour driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

@@

\subsection{Step 1}

@@

\noindent This first step might appear useless, but as of now we
already have made some choices with regard to the API of our library.
By giving a usage example, we were forced to think about which
arguments our function takes.  We can now run Doctest to verify that
the example works.

@@

\subsection{Step 2}

@@

\noindent Of course, this spec fails when we run it,

\begin{quote}
\small
\begin{verbatim}
$ runhaskell Fib.hs
fib
 - calculates arbitrary Fibonacci numbers FAILED [1]
\end{verbatim}
\end{quote}

\noindent so we add a working implementation.  Both Doctest and Hspec
report success after this.

@@

\subsection{Step 3}

As the seasoned Haskeller might have already noticed, our
implementation is quite inefficient, as can be proved by this
specification:

@@

\begin{quote}
\small
\begin{verbatim}
$ runhaskell Fib.hs
fib
 - calculates arbitrary Fibonacci numbers
 - is efficient FAILED [1]
\end{verbatim}
\end{quote}

@@

\subsection{Step 4}

>>>>

\subsection{Applying BDD to Haskell: An Example}
This section shows how behaviour driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

@@

\subsubsection{Step 1}

@@

\noindent This first step might appear excessively trivial, but as of now we
already have made some choices with regard to the API of our library.
By giving a usage example, we were forced to think about which
arguments our function takes.  We can now run Doctest to verify that
the example works.

@@

\subsubsection{Step 2}

@@

\noindent Of course this spec fails when we run it,

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs
fib
 - calculates arbitrary Fibonacci numbers FAILED [1]
\end{verbatim}
\end{quote}

\noindent so we add a working implementation.  Both Doctest and Hspec
report success after that.

@@

\subsubsection{Step 3}

As the seasoned Haskeller might have already noticed, our
implementation is quite inefficient, as made evident by this
specification:

@@

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs
fib
 - calculates arbitrary Fibonacci numbers
 - is efficient FAILED [1]
\end{verbatim}
\end{quote}

@@

\subsubsection{Step 4}
